---
title: "Presentation"
author: "JH"
date: '2023-01-03'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is the presentation for presenting the final data products for the Data Science Capstone.

The originl data is the text data provided by Swiftkey. You can access the data from [here](https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip). The three text files in the en_US folder are used as the data for this project.

The goal of this project is to use the text data as the basis, to create a shiny app that allow the user to input some words and automatically predict the next words. Detailed information can be found on [Coursera](https://www.coursera.org/learn/data-science-project?specialization=jhu-data-science&utm_source=gg&utm_medium=sem&utm_campaign=03-DataScience-JHU-US&utm_content=03-DataScience-JHU-US&campaignid=313639147&adgroupid=121203872804&device=c&keyword=&matchtype=b&network=g&devicemodel=&adpostion=&creativeid=507187136063&hide_mobile_promo&gclid=Cj0KCQjwvaeJBhCvARIsABgTDM4L9NH41XAn2Ef_1zplguykYRFzpAy5sStoHNe7I2GGEnl5jeGkGRwaAgAWEALw_wcB).

## Approaches 

The main r packacge used for cleaning the data is quanteda.


<font size="4">**1. Subset the data:** 40% of each text files are randomly sampled.</font>  
<font size="4">**2. Remove confounded:** Abbreviations like 'm,'t are replaced, and characters other than English removed.</font>  
<font size="4">**3. Tokenize the data:** Tokenize the data while removing punctuation, numbers, urls, etc.</font>  
<font size="4">**4. Stem the words:** Words are stemmed to avoid counting same words in different forms in multiple times.</font>  
<font size="4">**5. Ngrams analysis:** Perform Ngrams calculation and split the words in bigram and trigram for future analysis.</font>  
<font size="4">**6. Kneser Kny Smoothing:** Use Kneser-Ney smoothing methods to assign the probilities to each unigram, bigrams and trigrams.</font>  
<font size="4">**7. Predict the words:** Function will search the input in trigrams first then bigrams, if still no matches, one of the top 10 unigrams will be predicted.</font>


## Data samples {#slideID}
<style> 
  #slideID > p { 
    margin-top: -30px; 
  } 
</style>

<font size="4">The head of the uniwords, biwords and triwords data used in the project is displayed as followed.</font>
```{r cars, echo = F}
uni_words <- readRDS(file = "unidata")
bi_words <- readRDS(file = "bidata")
tri_words <- readRDS(file = "tridata")
```

<font size="4">**UniWords**</font>
```{r,echo=F}
head(uni_words,2)
```

<font size="4">**BiWords**</font>
```{r,echo=F}
bi_words[5:6,]
```

<font size="4">**TriWords**</font>
```{r,echo=F}
tri_words[100:101,]
```

## The Shiny APP

The Shiny App can be accessed from [here](https://jliao12.shinyapps.io/NLP_Next_Word_Prediction/).

- Put some words and the results will display automatically.
- Choose number of outcomes you would like to see.
- You can view the results is coming from which word set and the other possible outcomes from that data set.
- When open the link, the results may take a few second to display, thank you for your patience.
